### 2023-03-04 sections/papers.tex
Update papers.tex

\item{\small González-Bustamante. B. (2022, {\itshape forthcoming}). Quantitative Methods for Studying Elites: Practical Applications, Biases and Potential. {\itshape Revista Chilena de Derecho y Ciencia Política}. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv:} \\ \href{http://dx.doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}

>>>>

\item{\small González-Bustamante. B. (2022). Quantitative Methods for Studying Elites: Practical Applications, Biases and Potential. {\itshape Revista Chilena de Derecho y Ciencia Política, 13}(2), 12--44. {\footnotesize \scshape [in Spanish]}. {\scshape doi:} \href{https://doi.org/10.7770/rchdcp-V13N2-art2907}{\textcolor{blue}{10.7770/rchdcp-V13N2-art2907}}. {\scshape \footnotesize SocArXiv:} \href{http://dx.doi.org/10.31235/osf.io/5m2ur}{\textcolor{blue}{10.31235/osf.io/5m2ur}}.}\vspace{1mm}
